Selectively Remove Variables

### 2022-11-17 src/Selectively_remove_variables.Rmd
Update Selectively_remove_variables.Rmd

```{r}
fit2 <- predict(glm_Lasso, train.x)
true2 <- train.y
summary_Lasso_train <- eval_results(fit2, true2)
summary_Lasso_train
```
```{r}
plot_glmnet(lasso_model)
```

@@

```{r}
knitr::kable(summary_Ridge, digits = 3)
```
```{r}
summary(lm_4)
```

@@

Both the Ridge regression and LASSO regression models exhibit similar result metrics (MSE, MAE, MAPE, R^2). This result is expected.

```{r}
plot_glmnet(ridge_model)
```
###  3.2.3. Interpretation

The comparison between the three models suggests that `country.code` affects the models generated in a significant way.

>>>>

```{r}
fit2 <- predict(glm_Lasso, train.x)
true2 <- train.y
summary_Lasso_train <- eval_results(fit2, true2)
summary_Lasso_train
```

@@

```{r}
summary(lm_4)
```

@@

```{r}
knitr::kable(summary_Ridge, digits = 3)
```
The MSE for the LASSO regression model is slightly higher than that of the Ridge regression model. This to be expected, as the Ridge regression model aims for an improved accuracy while the LASSO model aims for an improved interpretability. Both models seem to exhibit very high R^2 value for both the training and testing dataset.

```{r}
plot_glmnet(lasso_model)
```
```{r}

```{r}
plot_glmnet(ridge_model)
```
```{r}
plot(lm_4, which = 5)
```
The `Residual vs Leverage` plot of `lm_4` suggests that heteroskedasticity might be present in the model. This means that the variance of the residuals is unequal over a range of observed values. This problem exists in the dataset rather than the models generated.
